\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-18 doc/mlsys_paper/paper.tex
fix and clarification: avoid confusion between the name 'ensmallen' and the experiment named 'ensmallen'

Next, we consider the linear regression example described in
Sec.~\ref{sec:linreg_example}.  For this task we use the first-order L-BFGS
optimizer~\cite{zhu1997algorithm}.  Using the same four packages, we implement
the linear regression objective and gradient.  For \texttt{\small ensmallen} we
implement a version with only \texttt{\small EvaluateWithGradient()}:
\texttt{\small ensmallen}.  We also implement a version with both \texttt{\small
Evaluate()} and \texttt{\small Gradient()}: \texttt{\small ensmallen}-2.  We
also use automatic differentiation for Julia via the \texttt{\small
ForwardDiff.jl}~\cite{RevelsLubinPapamarkou2016} package and for Python via the
\texttt{\small Autograd}~\cite{maclaurin2015autograd}
package.  For GNU Octave we use the \texttt{\small bfgsmin()} function.

>>>>

Next, we consider the linear regression example described in
Sec.~\ref{sec:linreg_example}.  For this task we use the first-order L-BFGS
optimizer~\cite{zhu1997algorithm}.  Using the same four packages, we implement
the linear regression objective and gradient.  For \texttt{\small ensmallen} we
implement a version with only \texttt{\small EvaluateWithGradient()},
denoted as \texttt{\small ensmallen-1}.  We also implement a version with both
\texttt{\small Evaluate()} and \texttt{\small Gradient()}: \texttt{\small ensmallen-2}.
We also use automatic differentiation for Julia via the \texttt{\small
ForwardDiff.jl}~\cite{RevelsLubinPapamarkou2016} package and for Python via the
\texttt{\small Autograd}~\cite{maclaurin2015autograd}
package.  For GNU Octave we use the \texttt{\small bfgsmin()} function.
